---
title: "Summaries"
author: "Galina M. Jönsson"
date: "17/01/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

## Record summaries - spatiotemporal coverage

### Temporal coverage of records

```{r temporal-spread, cache=TRUE, message=FALSE, warning=FALSE}
# Load spp_vis data (any would do), which contain all visits and whether or not each of the three species have been observed at that visit
spp_vis <- read.csv('../outputs/formattedData/spp_vis_merged_1kmgrid_date_year.csv', header=T, na.strings=c("","NA"))

# Load occDetdata giving each visits' site ID (grid cell), list length (numper of species observed) and time period (in this case year)
occDetdata_merged_1kmgrid_date_year <- read.csv('../outputs/formattedData/occDetdata_merged_1kmgrid_date_year.csv', header=T, na.strings=c("","NA"))

# Merge by visit
spp_vis <- merge(spp_vis, occDetdata_merged_1kmgrid_date_year, by="visit")

# Find unique visits
spp_vis <- unique(spp_vis)

# Create a species column
spp_vis$species <- as.factor(c("NA"))

# Subset each species' records and specify species
spp_vis_crabro <- subset(spp_vis, Vespa.crabro == "TRUE")
spp_vis_crabro$species <- c("Vespa crabro")
spp_vis_germanica <- subset(spp_vis, Vespula.germanica == "TRUE")
spp_vis_germanica$species <- c("Vespula germanica")
spp_vis_vulgaris <- subset(spp_vis, Vespula.vulgaris == "TRUE")
spp_vis_vulgaris$species <- c("Vespula vulgaris")

# V. vulgaris -> make a data frame with all sites with records of this species and the records' source to later map
require(dplyr)
spp_vis_vulgaris_source <- unique(spp_vis_vulgaris[,c('site','L')])
spp_vis_vulgaris_source <- spp_vis_vulgaris_source %>%
	group_by(site) %>%
  tally(L)

spp_vis_vulgaris_source$source <- spp_vis_vulgaris_source$n
spp_vis_vulgaris_source$source <- as.factor(as.character(spp_vis_vulgaris_source$source))
library(plyr)
# Revalue sources: 10 is NHM, less than 10 is BWARS and more thna 10 is both NHM and BWARS
spp_vis_vulgaris_source$source <- revalue(spp_vis_vulgaris_source$source, c("1"="BWARS", "10"="NHM", "11"="NHM+BWARS", "13"="NHM+BWARS", "16"="NHM+BWARS", "2"="BWARS", "3"="BWARS", "4"="BWARS", "6"="BWARS"))

# V. germanica -> make a data frame with all sites with records of this species and the records' source to later map
spp_vis_germanica_source <- unique(spp_vis_germanica[,c('site','L')])
spp_vis_germanica_source <- spp_vis_germanica_source %>%
	group_by(site) %>%
  tally(L)

spp_vis_germanica_source$source <- spp_vis_germanica_source$n
spp_vis_germanica_source$source <- as.factor(as.character(spp_vis_germanica_source$source))
library(plyr)
spp_vis_germanica_source$source <- revalue(spp_vis_germanica_source$source, c("1"="BWARS", "10"="NHM", "11"="NHM+BWARS", "13"="NHM+BWARS", "2"="BWARS", "3"="BWARS", "4"="BWARS", "5"="BWARS", "6"="BWARS"))

# V. crabro -> make a data frame with all sites with records of this species and the records' source to later map
spp_vis_crabro_source <- unique(spp_vis_crabro[,c('site','L')])
spp_vis_crabro_source <- spp_vis_crabro_source %>%
	group_by(site) %>%
  tally(L)

spp_vis_crabro_source$source <- spp_vis_crabro_source$n
  
spp_vis_crabro_source$source <- as.factor(as.character(spp_vis_crabro_source$source))
library(plyr)
spp_vis_crabro_source$source <- revalue(spp_vis_crabro_source$source, c("1"="BWARS", "10"="NHM", "11"="NHM+BWARS", "13"="NHM+BWARS", "14"="NHM+BWARS", "2"="BWARS", "3"="BWARS", "4"="BWARS", "5"="BWARS", "6"="BWARS"))

# row bind each subsetted species' dataframe
spp_vis <- rbind(spp_vis_crabro, spp_vis_germanica)
spp_vis <- rbind(spp_vis, spp_vis_vulgaris)

# Rename site column to grid1km, as it shows the 1x1km gridref
spp_vis$grid1km <- as.character(spp_vis$site)
#spp_vis$grid1km <- as.factor(substr(spp_vis$grid1km,1,nchar(spp_vis$grid1km)-6))

# Make a column collapsing the content of the first three logical columns
spp_vis$speciesID <-  as.factor(paste(spp_vis$Vespa.crabro , spp_vis$Vespula.germanica, spp_vis$Vespula.vulgaris))
# Rename levels to make sense
require(plyr)
spp_vis$speciesID <- revalue(spp_vis$speciesID, c("FALSE FALSE TRUE"="V. vulgaris", "FALSE TRUE FALSE"="V. germanica", "FALSE TRUE TRUE"="V. vulgaris + V. germanica", "TRUE FALSE FALSE"="V. crabro", "TRUE FALSE TRUE"="V. crabro + V. vulgaris", "TRUE TRUE FALSE"="V. crabro + V. germanica", "TRUE TRUE TRUE"="V. crabro + V. vulgaris + V. germanica"))

# Add rows with all unique visits
spp_vis_unique <- spp_vis
spp_vis_unique$Vespa.crabro <- "NA"
spp_vis_unique$Vespula.germanica <- "NA"
spp_vis_unique$Vespula.vulgaris <- "NA"
spp_vis_unique$species <- "Total"
#spp_vis_unique <- unique(spp_vis_unique)  
spp_vis_unique <- droplevels(spp_vis_unique)
spp_vis <- rbind(spp_vis, spp_vis_unique)

# Make LL column a source column
spp_vis$L <- as.factor(spp_vis$L)
require(plyr)
spp_vis$L <- revalue(spp_vis$L, c("1"="BWARS", "2"="BWARS", "3"="BWARS", "10"="NHM"))
colnames(spp_vis)[colnames(spp_vis)=="L"] <- "Source"

# Make additional species column
spp_vis$species2 <- as.factor(spp_vis$species)
require(plyr)
spp_vis$species2 <- revalue(spp_vis$species2, c("Vespa crabro"="italic('V. crabro')", "Vespula germanica"="italic('V. germanica')", "Vespula vulgaris"="italic('V. vulgaris')", "Total"="textstyle('Total')"))

spp_vis$speciesOrdered = factor(spp_vis$species2, levels=c("italic('V. vulgaris')","italic('V. germanica')", "italic('V. crabro')", "textstyle('Total')" , "NA"))

spp_vis$year <- spp_vis$TP+1899

# Plot years
require(ggplot2)
require(viridis)
ggplot(spp_vis, aes(x=year, fill=Source, color=Source)) + 
  scale_fill_manual(values = c("#999999", "#D55E00")) +
  scale_color_manual(values = c("#999999", "#D55E00")) +
  facet_grid(~ speciesOrdered, labeller=label_parsed) +
  geom_bar(position="identity", alpha=0.5) + labs(y="Number of Records", x = "Year") +
  theme_bw() +
  scale_y_sqrt() +
  #scale_fill_brewer(palette = "Set3") + 
  #scale_fill_manual(values=viridis(2)) +
  #scale_fill_manual("legend", values = viridis(2)) +
  theme(text = element_text(size=18),
        axis.text.x = element_text(angle=90, hjust=1))
```

### Temporal coverage of records

```{r spatial-spread, cache=TRUE, message=FALSE, warning=FALSE}

# 10 km grid cells
require(BRCmap)
spp_vis$grid10km <- reformat_gr(spp_vis$grid1km, prec_out = 10000, precision = NULL, pad_gr = FALSE)

spp_vis_10km_grids2 <- spp_vis %>% 
      group_by(grid10km) %>% 
      tally()
colnames(spp_vis_10km_grids2)[colnames(spp_vis_10km_grids2)=="n"] <- "nVisits"


spp_vis_10km_grids2 <- merge(spp_vis_10km_grids2, (unique(spp_vis[,c('grid10km','species')]) %>% 
      group_by(grid10km) %>% 
      tally()) , by="grid10km",all.x=TRUE)
colnames(spp_vis_10km_grids2)[colnames(spp_vis_10km_grids2)=="n"] <- "nSpecies"

spp_vis_10km_grids <- merge(spp_vis_10km_grids2, (unique(spp_vis[,c('grid10km','TP')]) %>% 
      group_by(grid10km) %>% 
      tally()) , by="grid10km",all.x=TRUE)
colnames(spp_vis_10km_grids)[colnames(spp_vis_10km_grids)=="n"] <- "nYears"

# Create range categories
spp_vis_10km_grids$nVisitsCat <- cut(spp_vis_10km_grids$nVisits, breaks=c(0, 2, 5, 10, 20, 50, Inf), labels=c("2", "3-5", "6-10", "11-20", "21-50", "50-190"))
spp_vis_10km_grids$nYearsCat <- cut(spp_vis_10km_grids$nYears, breaks=c(0, 2, 3, 5, 10, 15, 20, Inf), labels=c("2", "3", "4-5", "6-10", "11-15", "16-20", "21-40"))
# Make number of species a factor
spp_vis_10km_grids$nSpecies <- as.factor(spp_vis_10km_grids$nSpecies)


# Plot maps
require(BRCmap)
require(viridis)
require(ggthemes)
# Load UK data
data(UK)

# Plot UK outline
plot_GIS(UK$britain, main = "Spatial distribution of wasp records at 10 km2 by number of species", xlim = c(100000,700000), ylim = c(0,700000), new.window = FALSE, show.grid = FALSE, show.axis = FALSE)
# Add squares to map colouring by number of species
BRCmap::plotUK_gr_cats(spp_vis_10km_grids$grid10km, spp_vis_10km_grids$nSpecies, att_col = c("#FDE725FF", "#21908CFF","#440154FF"), border = FALSE)


# Plot UK outline
plot_GIS(UK$britain, main = "Spatial distribution of wasp records at 10 km2 by number of records", xlim = c(100000,700000), ylim = c(0,700000), new.window = FALSE, show.grid = FALSE, show.axis = FALSE)
# Add squares to map colouring by number of species
BRCmap::plotUK_gr_cats(spp_vis_10km_grids$grid10km, spp_vis_10km_grids$nVisitsCat, att_col = c("#FDE725FF","#7AD151FF","#22A884FF", "#2A788EFF", "#414487FF","#440154FF"), border = FALSE)



plot_GIS(UK$britain, main = "Spatial distribution of V. vulgaris records at 10 km2", xlim = c(100000,700000), ylim = c(0,700000), new.window = FALSE, show.grid = FALSE, show.axis = FALSE)
# Add squares to map colouring by number of species
#BRCmap::plotUK_gr(reformat_gr(spp_vis_vulgaris$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), col="grey25", border = FALSE)
BRCmap::plotUK_gr_cats(reformat_gr(spp_vis_vulgaris_source$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), spp_vis_vulgaris_source$source, att_col = (colorblind_pal()(3)), border = FALSE)


plot_GIS(UK$britain, main = "Spatial distribution of V. germanica records at 10 km2", xlim = c(100000,700000), ylim = c(0,700000), new.window = FALSE, show.grid = FALSE, show.axis = FALSE)
# Add squares to map colouring by number of species
#BRCmap::plotUK_gr(reformat_gr(spp_vis_vulgaris$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), col="grey25", border = FALSE)
BRCmap::plotUK_gr_cats(reformat_gr(spp_vis_germanica_source$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), spp_vis_germanica_source$source, att_col = (colorblind_pal()(3)), border = FALSE)

plot_GIS(UK$britain, main = "Spatial distribution of V. crabro records at 10 km2", xlim = c(100000,700000), ylim = c(0,700000), new.window = FALSE, show.grid = FALSE, show.axis = FALSE)
# Add squares to map colouring by number of species
#BRCmap::plotUK_gr(reformat_gr(spp_vis_vulgaris$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), col="grey25", border = FALSE)
BRCmap::plotUK_gr_cats(reformat_gr(spp_vis_germanica_source$site, prec_out = 10000, precision = NULL, pad_gr = FALSE), spp_vis_germanica_source$source, att_col = (colorblind_pal()(3)), border = FALSE)
```



## General summaries

### Rhat
First I test whether all models' occupancy estimates have converged (Rhat<1.1) using the function summarise_Rhat (see function description in function-summarise_Rhat.R for details).
```{r summary-rhat, message=FALSE}
# Load packages
library(knitr)
library(kableExtra)

# Load the function
source("../analyses/function-summarise_Rhat.R")

# Run function to find whether model estimates have converged or not
RhatSum <- summarise_Rhat("../outputs/modelOutputs")

# Show summary tables
kable(RhatSum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
The table shows that all V. germanica (file names ending with "_vg.rds") at 1 year temporal resolutions (file names ending with "year_vg.rds") have not converged. 

### Sample sizes
Load the tables summarising sample sizes, remove V. germanica ouputs at 1 year temporal resolutions and show the tables
```{r summary-tables, cache=TRUE, message=FALSE}
# Load packages
library("boot")

# Load summary tables
modelSummary <- read.csv("../outputs/SummaryTables/modelSummary.csv", header=T, as.is = TRUE, na.strings=c("","NA")) 
sppLevelSummary <- read.csv("../outputs/SummaryTables/sppLevelSummary.csv", header=T, as.is = TRUE, na.strings=c("","NA")) 

# Remove V. germanica ouputs at 1 year temporal resolutions
sppLevelSummary <- sppLevelSummary  %>% 
  filter(!(Species=="Vespula germanica" & closurePer=="1yr"))

# Show summary tables
kable(sppLevelSummary) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(modelSummary) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```