---
title: "Bayesian Occupancy Models"
author: "Galina M. Jönsson"
date: "17/01/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---


## general summaries

### Rhat
First I test whether all models' occupancy estimates have converged (Rhat<1.1) using the function summarise_Rhat (see function description in function-summarise_Rhat.R for details).
```{r summary-rhat, message=FALSE}
# Load packages
library(knitr)
library(kableExtra)

# Load the function
source("../analyses/function-summarise_Rhat.R")

# Run function to find whether model estimates have converged or not
RhatSum <- summarise_Rhat("../outputs/modelOutputs")

# Show summary tables
kable(RhatSum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
The table shows that all V. germanica (file names ending with "_vg.rds") at 1 year temporal resolutions (file names ending with "year_vg.rds") have not converged. 

### Sample sizes
Load the tables summarising sample sizes, remove V. germanica ouputs at 1 year temporal resolutions and show the tables
```{r summary-tables, cache=TRUE, message=FALSE}
# Load packages
library("boot")

# Load summary tables
modelSummary <- read.csv("../outputs/SummaryTables/modelSummary.csv", header=T, as.is = TRUE, na.strings=c("","NA")) 
sppLevelSummary <- read.csv("../outputs/SummaryTables/sppLevelSummary.csv", header=T, as.is = TRUE, na.strings=c("","NA")) 

# Remove V. germanica ouputs at 1 year temporal resolutions
sppLevelSummary <- sppLevelSummary  %>% 
  filter(!(Species=="Vespula germanica" & closurePer=="1yr"))

# Show summary tables
kable(sppLevelSummary) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(modelSummary) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```