---
title: "Bayesian Occupancy Models"
author: "Galina M. Jönsson"
date: "17/01/2020"
output: html_document
---


## general summaries

### Rhat
First I test whether all models' occupancy estimates have converged (Rhat<1.1) using the function summarise_Rhat (see function description in function-summarise_Rhat.R for details).
```{r summary-rhat, cache=TRUE, message=FALSE}
# Load packages
library(knitr)
library(kableExtra)

# Load the function
source("../analyses/function-summarise_Rhat.R")

# Run function to find whether model estimates have converged or not
RhatSum <- summarise_Rhat("../outputs/modelOutputs")

# Show summary tables
kable(RhatSum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```


Load the tables summarising sample sizes below
```{r summary-tables, cache=TRUE, message=FALSE}
# Load packages
library(knitr)
library(kableExtra)
library("boot")

# First, inverse logit alphaPrec and alphaPPrec
sppModelSumDF$alphaPrec <- inv.logit(sppModelSumDF$alphaPrec)
sppModelSumDF$alphaPPrec <- inv.logit(sppModelSumDF$alphaPPrec)

# Save modelSumDF
#write.csv(modelSumDF, '../outputs/SummaryTables/modelSummary.csv')

# Save sppModelSumDF
#write.csv(sppModelSumDF, '../outputs/SummaryTables/sppLevelSummary.csv')

# Show summary tables
kable(sppModelSumDF) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(modelSumDF) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```